High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-19 notebooks/mnist.qmd
:cry:

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 100])
n_hidden = 32
activation = Flux.relu
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden),
    BatchNorm(n_hidden, activation),
    Dense(n_hidden, n_out),
    BatchNorm(n_out)
)
# builder = MLJFlux.Short(n_hidden=n_hidden, dropout=0.2, σ=activation)
# builder = MLJFlux.MLP(
#     hidden=(
#         n_hidden,
#         n_hidden,
#         n_hidden,
#     ), 
#     σ=activation
# )
α = [1.0,1.0,5e-1]

@@

# Joint Energy Model:
𝒟x = Uniform(0,1)
𝒟y = Categorical(ones(output_dim) ./ output_dim)
sampler = ConditionalSampler(𝒟x, 𝒟y, input_size=(input_dim,), batch_size=batch_size)
jem = JointEnergyClassifier(
    sampler;
    builder=builder,
    batch_size=batch_size,
    finaliser=x -> x,
    loss=Flux.Losses.logitcrossentropy,
    jem_training_params=(
        α=α,verbosity=10,
        use_gen_loss=false,
        use_reg_loss=false,
    ),
    sampling_steps=20,
    epochs=epochs,
)

>>>>

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 100])
n_hidden = 32
activation = Flux.relu
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden),
    BatchNorm(n_hidden, activation),
    Dense(n_hidden, n_out),
)
# builder = MLJFlux.Short(n_hidden=n_hidden, dropout=0.2, σ=activation)
# builder = MLJFlux.MLP(
#     hidden=(
#         n_hidden,
#         n_hidden,
#         n_hidden,
#     ), 
#     σ=activation
# )
α = [1.0,1.0,1e-2]

@@

# Joint Energy Model:
𝒟x = Uniform(0,1)
𝒟y = Categorical(ones(output_dim) ./ output_dim)
sampler = ConditionalSampler(𝒟x, 𝒟y, input_size=(input_dim,), batch_size=batch_size)
jem = JointEnergyClassifier(
    sampler;
    builder=builder,
    batch_size=batch_size,
    finaliser=x -> x,
    loss=Flux.Losses.logitcrossentropy,
    jem_training_params=(
        α=α,verbosity=10,
        # use_gen_loss=false,
        # use_reg_loss=false,
    ),
    sampling_steps=20,
    epochs=epochs,
)
